Zero-shot task adaptation by homoiconic meta-mapping

### 2019-11-11 writing/homoiconic_meta_mapping_appendix.tex
Other change back

\subsection{Source repositories}
(Will be included in de-anonymized version.)
%The full code for the experiments and analyses can be found on github:
%\begin{itemize}
%\item \url{https://github.com/lampinen/polynomials}
%    \begin{itemize}
%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
%    \end{itemize}
%\item \url{https://github.com/lampinen/meta_cards} 
%\end{itemize}
\section{Numerical results} \label{app_numerical_results}
In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures. Tables were generated with stargazer \citep{Hlavac2018}. \par

>>>>

\subsection{Source repositories}
The full code for the experiments and analyses can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
\section{Numerical results} \label{app_numerical_results}
In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures. Tables were generated with stargazer \citep{Hlavac2018}. \par
